week getbackontrack

### 2024-11-09 RSienatry.Rmd
restructuredprepdescriptivesandrsiena

---
title: "Plotting plots and Hotzenplotz"
author: "Verooo"
date: "2024-11-05"
output: html_document
---

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

@@

Meeting with Jochem

look at publications website (sunbelt workshop)

@@

#install.packages("data.table")
require(data.table)  # mainly for faster data handling
# install.packages('xml2')
require(xml2)
# install.packages('rvest')
require(rvest)
require(igraph)

require(ggraph)
#install.packages('visNetwork')
require(visNetwork)
#install.packages('threejs')
require(threejs)
#install.packages('networkD3')
require(networkD3)

@@

# Gender

## saving data for each deapartment

```{r}
#inspecting scholars_20240924.rda object
#df_ego <- do.call(rbind.data.frame, scholars$demographics)
#unique(df_ego$discipline.22)

# save the output of your function
testsoc  <- fcolnet(data = scholars, 
                university = "RU", 
                discipline = "sociology", 
                waves = list(c(2015, 2018), c(2019, 2023)),

                            type = c("first"))

# I DONT KNOW HOW TO MAKE ALL SCHOLARS BE PART OF SAME FUNCTION ("sociology"+ "political science" does not work...)

testpolsci <- fcolnet(data = scholars, 
                university = "RU", 
                discipline = "political science", 
                waves = list(c(2015, 2018), c(2019, 2023)), 
                type = c("first"))
```

#### soc department save

```{r}
soc_nets <- testsoc$nets

df_ego_demo <- testsoc$data$demographics
df_ego_oa <- testsoc$data$scholars_oa
df_ego_works <- testsoc$data$works

# DEMO
  str(df_ego_demo, 1)

  df_ego_demo <- do.call(rbind.data.frame, df_ego_demo)
  df_ego_demo[[1]]

# OA
  #str(df_ego_oa, 1)
  df_ego_oa[[1]]
  df_ego_oa <- do.call(rbind.data.frame, df_ego_oa)

  # --> EGO DATAFRAME with demo and oa (sociology)
  ?join.data.frame
  df_soc_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))

  rownames(soc_nets[1,,]) == df_soc_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
  # --> yes, the correct ones!!!

  df_ego_works[[1]]$author 
#authors of all the works that first scholar (here: Ana Macanovic) is part of

#### polsci department save

```{r}
# dependent
# pol_net <- sienaDependent(net_pol_array)

# dependent 
pol_nets <- testpolsci$nets

df_pol_ego_demo <- testpolsci$data$demographics
df_pol_ego_oa <- testpolsci$data$scholars_oa
df_pol_ego_works <- testpolsci$data$works

# DEMO
  #str(df_pol_ego_demo, 1)

  df_pol_ego_demo <- do.call(rbind.data.frame, df_pol_ego_demo)
  df_pol_ego_demo[[1]]

# OA
  #str(df_pol_ego_oa, 1)
  df_pol_ego_oa[[1]]
  df_pol_ego_oa <- do.call(rbind.data.frame, df_pol_ego_oa)

# --> EGO DATAFRAME with demo and oa (political science)
  df_pol_ego <- left_join(df_pol_ego_demo, df_pol_ego_oa, by = join_by(au_id == id))

  rownames(pol_nets[1,,]) == df_pol_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
  # --> yes, the correct ones!!!
```

### gender - sociology department

```{r gender s}
df_soc_ego$Naam # list of all names in sociology department

df_soc_ego$gender <- c(0,1,0,1,0,0,1,1,0,0,
                       0,1,1,0,1,0,1,1,1,1,
                       0,1,1,0,1,1,0,1,0,1,
                       0,1,0,0,0,0,0,0,1,0,
                       0,1,1,1,0,1,0,1,0,0) 
# manually filled in gender 0 = woman, 1 = man, based on majority given in NL voornamen bank

# check if it went smoothly 
# view(df_soc_ego[c('Naam', 'gender', 'au_id')])

# fsave(df_soc_ego)

### gender - polsci

```{r gender p}
df_pol_ego$Naam # list of all names

df_pol_ego$gender <- c(1,0,1,0,0,0,1,0,1,0,
                       1,1,0,0,1,1,1,0,0,1,
                       0,1,1,0,0,1,1,1,0,0,
                       0,0,0,1,1,0,0,1,1,0,
                       0,0,0,1,0,1,1,1,0,0,0) 
    # manually filled in gender 0 = woman, 1 = man, based on majority given in NL voornamen bank, Guangyu was not in name bank but based on the employee-picture of RU, this person presents feminine, thus I assumed 0.

# check if it went smoothly 
# view(df_pol_ego[c('Naam', 'gender', 'au_id')])

#covariate 
# gender <- coCovar(df_ego$gender)

# fsave(df_pol_ego)
```

### save gender data sets

```{r gender data}
soc_gender <- fload("./data/processed/df_soc_ego_20241105.rda")
pol_gender <- fload("./data/processed/df_pol_ego_20241105.rda")
```

### Combine data (gender)

```{r combine gender set}
df <- test$data # make dataset with all data 
df_ego <- do.call(rbind.data.frame, df$demographics) # data set with demographic information

soc_gender <- soc_gender[,c("Naam", "gender")] # selecting only the content we need
pol_gender <- pol_gender[,c("Naam", "gender")] # selecting only the content we need

gender <- rbind(soc_gender, pol_gender) # combining the gender data sets

df_ego <- df_ego %>% 
            left_join(gender) #dcombining data set of gender with the one with demographic information 
```

# H-index 
Credits to Lucan Bovens for the code.

```{r h-index}
# Add h-index and i10-index columns to df_ego
df_ego <- df_ego %>%
  mutate(h_index = NA_real_, i10_index = NA_real_)

# Get H-index and i10-index 
get_openalex_metrics <- function(openalex_id) {
  url <- paste0("https://api.openalex.org/authors/", openalex_id)
  author_data <- tryCatch({
    jsonlite::fromJSON(url)
  }, error = function(e) {
    message(paste("Error fetching data for OpenAlex ID:", openalex_id))
    return(NULL)
  })

  if (!is.null(author_data)) {
    h_index <- author_data$summary_stats$h_index
    i10_index <- author_data$summary_stats$i10_index
    works_count <- author_data$works_count
    cited_by_count <- author_data$cited_by_count
    return(list(h_index = h_index, i10_index = i10_index, works_count = works_count, cited_by_count = cited_by_count))
  } else {
    return(list(h_index = NA, i10_index = NA, works_count = NA, cited_by_count = NA))
  }
}

# Loop for each scholar 
for (i in 1:nrow(df_ego)) {
  openalex_id <- df_ego$au_id[i]  # assuming au_id is the OpenAlex ID in df_ego
  metrics <- get_openalex_metrics(openalex_id)
  df_ego$h_index[i] <- metrics$h_index
  df_ego$i10_index[i] <- metrics$i10_index
  df_ego$works_count[i] <- metrics$works_count
  df_ego$cited_by_count[i] <- metrics$cited_by_count
}

# View updated df_ego with h-index and i10-index
view(df_ego[c('au_id','Naam','gender','h_index','i10_index')])

# Quick RSiena

```{r RSiena}
#step1 data
wave1 <- test$nets[1,,]
wave2 <- test$nets[2,,]

@@

```{r RSiena2}
# put the nets in an array
net_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))
#dependent
nets <- sienaDependent(net_array)

@@

#define effects structure 
myeff <- getEffects(mydata)

# skipped initial description part

@@

```{r RSiena-model estimate}
# estimate the model 
model1 <- siena07(myAlgorithm, data = mydata, effects = myeff, returnDeps = TRUE)
#latter needed for GOF

@@

# Make it a directed network 
# focus: writing, h index, 
# model interpretation

@@

# Plotting
```{r}
test_w1 <- igraph::graph_from_adjacency_matrix(
  test$nets[1,,], # first wave of data. 
  # (thus I select the array of networks and take the first matrix)
  mode = c("directed"),
  weighted = NULL,
  diag = FALSE,
  add.colnames = NULL,
  add.rownames = NULL)

plot(test_w1,
     vertex.label = NA,
     edge.width = 0.2,
     edge.arrow.size =0.2)
```

```{r}
names(df_ego) #see labels of variables

plot(test_w1,
vertex.color = ifelse(df_ego$gender == 1, "red", "blue"), # now, I can use actor attributes for plotting.
# here: if gender = 1 (aka man) then red dot, if not then blue 
vertex.label = NA,
edge.width = 0.2,
edge.arrow.size =0.2)

# if you dont want plot to turn, save the layout (look at SNASS)
```

>>>>

---
title: "RSienatry"
author: "Verooo"
date: "2024-11-08"
output: html_document
---
```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

@@

@@

#install.packages("data.table")
require(data.table)  # mainly for faster data handling
# install.packages('xml2')
require(xml2)
# install.packages('rvest')
require(rvest)
require(igraph)
require(ggraph)

#install.packages('visNetwork')
require(visNetwork)
#install.packages('threejs')
require(threejs)
#install.packages('networkD3')
require(networkD3)

@@

## Step 1: Define data
```{r RSiena}
#step1 data
wave1 <- test$nets[1,,]
wave2 <- test$nets[2,,]

@@

```{r RSiena define 1}
# put the nets in an array
net_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))
#dependent
nets <- sienaDependent(net_array)
```

```{r RSiena define 2}

df_ego <- fload("./data/processed/df_ego_20241108.rda") #make sure to lead fload first ofcourse

@@

## Step 2: Make effects structure 
```{r RSiena myeff}
#define effects structure 
myeff <- getEffects(mydata)

## Step 3: initial description (skipped)
Nothing for now. :)

## Step 4: Specify model 
```{r RSiena spec mod}

@@

## Step 5: Estimate model 
```{r RSiena-model estimate, eval = FALSE}
# estimate the model 
model1 <- siena07(myAlgorithm, data = mydata, effects = myeff, returnDeps = TRUE)
#latter needed for GOF

@@

# Make it a directed network 
# focus: writing, 
# model interpretation

@@

### 2024-11-09 datapreptrynew.Rmd
restructuredprepdescriptivesandrsiena

---
title: "Plotting plots and Hotzenplotz"
author: "Verooo"
date: "2024-11-05"
output: html_document
---

@@

@@

## saving data for each deapartment

@@

# I DONT KNOW HOW TO MAKE ALL SCHOLARS BE PART OF SAME FUNCTION ("sociology"+ "political science" does not work...)

@@

  # --> EGO DATAFRAME with demo and oa (sociology)
  ?join.data.frame
  df_soc_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))

@@

# H-index 
Credits to Lucan Bovens for the code.

@@

@@

# Quick RSiena

```{r RSiena}
#step1 data
wave1 <- test$nets[1,,]
wave2 <- test$nets[2,,]

#put diagonals to zero 
diag(wave1) <- 0
diag(wave2) <- 0
# we want a binary tie (not a weighted tie)
wave1[wave1 > 1] <- 1
wave2[wave2 > 1] <- 1
```

```{r RSiena2}
# put the nets in an array
net_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))
#dependent
nets <- sienaDependent(net_array)

#put gender in object 
gender <- df_ego$gender
#covariate
gender_RS <- coCovar(gender) # gender as covariate in Rsiena

#put h-index in object 
h_index <- df_ego$h_index
df_ego$h_index
#covarite 2
h_index_RS <- coCovar(h_index) # h_index as covariate in RSiena

#define data 
mydata <- sienaDataCreate(nets, gender_RS, h_index_RS)

#define effects structure 
myeff <- getEffects(mydata)

# skipped initial description part

myeff <- includeEffects(myeff, isolateNet, inPop, outAct)

myeff <- includeEffects(myeff, egoX, altX, sameX, interaction1 = "gender_RS")
#include effect of h index later too etc
#look up which effects to iclude

myAlgorithm <- sienaAlgorithmCreate(modelType = c(nets=6), projname = "proProject")
# undirected: model 6 "additive model", #check manual for this
```

```{r RSiena-model estimate}
# estimate the model 
model1 <- siena07(myAlgorithm, data = mydata, effects = myeff, returnDeps = TRUE)
#latter needed for GOF

model1

# output:  convergence ration NA probably bc we chose all ties to be included (type = "all") earlier
# we can go back and change that or change it here in the myAlgorithm function

# Make it a directed network 
# focus: writing, h index, 
# model interpretation

# Plotting
```{r}
test_w1 <- igraph::graph_from_adjacency_matrix(
  test$nets[1,,], # first wave of data. 
  # (thus I select the array of networks and take the first matrix)
  mode = c("directed"),
  weighted = NULL,
  diag = FALSE,
  add.colnames = NULL,
  add.rownames = NULL)

plot(test_w1,
     vertex.label = NA,
     edge.width = 0.2,
     edge.arrow.size =0.2)
```

```{r}
names(df_ego) #see labels of variables

plot(test_w1,
vertex.color = ifelse(df_ego$gender == 1, "red", "blue"), # now, I can use actor attributes for plotting.
# here: if gender = 1 (aka man) then red dot, if not then blue 
vertex.label = NA,
edge.width = 0.2,
edge.arrow.size =0.2)

# if you dont want plot to turn, save the layout (look at SNASS)
```

>>>>

---
title: "datapreptrynew"
author: "Verooo"
date: "2024-11-08"
output: html_document
---

@@

 note to self:look at publications website (sunbelt workshop)

@@

## saving data for each department 
This part, despite being lengthy and principally unnecessary, needed to stay in my code for the sake of transparency. AFterall, this code is what accumulated in the gender-data of each department in my data set.

@@

@@

  # --> EGO DATAFRAME with demo and oa (sociology)

  df_soc_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))

@@

# H-index

Credits to Lucan Bovens for the code.

@@

# fsave(df_ego)

@@

### 2024-11-09 descriptivestry.Rmd
restructuredprepdescriptivesandrsiena

---
title: "Plotting plots and Hotzenplotz"
author: "Verooo"
date: "2024-11-05"
output: html_document
---

@@

```{r data}
scholars <- fload("./data/processed/scholars_20240924.rda") #make sure to lead fload first ofcourse
```

```{r saving output}
# save the output of your function

@@

# USE not all but first or last so the ties are directed from "perspective" of first author of the publications 
# usually first most prestige

@@

# Gender

## saving data for each deapartment

```{r}
#inspecting scholars_20240924.rda object
#df_ego <- do.call(rbind.data.frame, scholars$demographics)
#unique(df_ego$discipline.22)

# save the output of your function
testsoc  <- fcolnet(data = scholars, 
                university = "RU", 
                discipline = "sociology", 
                waves = list(c(2015, 2018), c(2019, 2023)),

                            type = c("first"))

# I DONT KNOW HOW TO MAKE ALL SCHOLARS BE PART OF SAME FUNCTION ("sociology"+ "political science" does not work...)

testpolsci <- fcolnet(data = scholars, 
                university = "RU", 
                discipline = "political science", 
                waves = list(c(2015, 2018), c(2019, 2023)), 
                type = c("first"))
```

#### soc department save

```{r}
soc_nets <- testsoc$nets

df_ego_demo <- testsoc$data$demographics
df_ego_oa <- testsoc$data$scholars_oa
df_ego_works <- testsoc$data$works

# DEMO
  str(df_ego_demo, 1)

  df_ego_demo <- do.call(rbind.data.frame, df_ego_demo)
  df_ego_demo[[1]]

# OA
  #str(df_ego_oa, 1)
  df_ego_oa[[1]]
  df_ego_oa <- do.call(rbind.data.frame, df_ego_oa)

  # --> EGO DATAFRAME with demo and oa (sociology)
  ?join.data.frame
  df_soc_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))

  rownames(soc_nets[1,,]) == df_soc_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
  # --> yes, the correct ones!!!

  df_ego_works[[1]]$author 
#authors of all the works that first scholar (here: Ana Macanovic) is part of

@@

#### polsci department save

```{r}
# dependent
# pol_net <- sienaDependent(net_pol_array)

# dependent 
pol_nets <- testpolsci$nets

df_pol_ego_demo <- testpolsci$data$demographics
df_pol_ego_oa <- testpolsci$data$scholars_oa
df_pol_ego_works <- testpolsci$data$works

# DEMO
  #str(df_pol_ego_demo, 1)

  df_pol_ego_demo <- do.call(rbind.data.frame, df_pol_ego_demo)
  df_pol_ego_demo[[1]]

# OA
  #str(df_pol_ego_oa, 1)
  df_pol_ego_oa[[1]]
  df_pol_ego_oa <- do.call(rbind.data.frame, df_pol_ego_oa)

# --> EGO DATAFRAME with demo and oa (political science)
  df_pol_ego <- left_join(df_pol_ego_demo, df_pol_ego_oa, by = join_by(au_id == id))

  rownames(pol_nets[1,,]) == df_pol_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
  # --> yes, the correct ones!!!
```

### gender - sociology department

```{r gender s}
df_soc_ego$Naam # list of all names in sociology department

df_soc_ego$gender <- c(0,1,0,1,0,0,1,1,0,0,
                       0,1,1,0,1,0,1,1,1,1,
                       0,1,1,0,1,1,0,1,0,1,
                       0,1,0,0,0,0,0,0,1,0,
                       0,1,1,1,0,1,0,1,0,0) 
# manually filled in gender 0 = woman, 1 = man, based on majority given in NL voornamen bank

# check if it went smoothly 
# view(df_soc_ego[c('Naam', 'gender', 'au_id')])

# fsave(df_soc_ego)

@@

### gender - polsci

```{r gender p}
df_pol_ego$Naam # list of all names

df_pol_ego$gender <- c(1,0,1,0,0,0,1,0,1,0,
                       1,1,0,0,1,1,1,0,0,1,
                       0,1,1,0,0,1,1,1,0,0,
                       0,0,0,1,1,0,0,1,1,0,
                       0,0,0,1,0,1,1,1,0,0,0) 
    # manually filled in gender 0 = woman, 1 = man, based on majority given in NL voornamen bank, Guangyu was not in name bank but based on the employee-picture of RU, this person presents feminine, thus I assumed 0.

# check if it went smoothly 
# view(df_pol_ego[c('Naam', 'gender', 'au_id')])

#covariate 
# gender <- coCovar(df_ego$gender)

# fsave(df_pol_ego)
```

### save gender data sets

```{r gender data}
soc_gender <- fload("./data/processed/df_soc_ego_20241105.rda")
pol_gender <- fload("./data/processed/df_pol_ego_20241105.rda")
```

### Combine data (gender)

```{r combine gender set}
df <- test$data # make dataset with all data 
df_ego <- do.call(rbind.data.frame, df$demographics) # data set with demographic information

soc_gender <- soc_gender[,c("Naam", "gender")] # selecting only the content we need
pol_gender <- pol_gender[,c("Naam", "gender")] # selecting only the content we need

gender <- rbind(soc_gender, pol_gender) # combining the gender data sets

df_ego <- df_ego %>% 
            left_join(gender) #dcombining data set of gender with the one with demographic information 
```

# H-index 
Credits to Lucan Bovens for the code.

```{r h-index}
# Add h-index and i10-index columns to df_ego
df_ego <- df_ego %>%
  mutate(h_index = NA_real_, i10_index = NA_real_)

# Get H-index and i10-index 
get_openalex_metrics <- function(openalex_id) {
  url <- paste0("https://api.openalex.org/authors/", openalex_id)
  author_data <- tryCatch({
    jsonlite::fromJSON(url)
  }, error = function(e) {
    message(paste("Error fetching data for OpenAlex ID:", openalex_id))
    return(NULL)
  })

  if (!is.null(author_data)) {
    h_index <- author_data$summary_stats$h_index
    i10_index <- author_data$summary_stats$i10_index
    works_count <- author_data$works_count
    cited_by_count <- author_data$cited_by_count
    return(list(h_index = h_index, i10_index = i10_index, works_count = works_count, cited_by_count = cited_by_count))
  } else {
    return(list(h_index = NA, i10_index = NA, works_count = NA, cited_by_count = NA))
  }
}

# Loop for each scholar 
for (i in 1:nrow(df_ego)) {
  openalex_id <- df_ego$au_id[i]  # assuming au_id is the OpenAlex ID in df_ego
  metrics <- get_openalex_metrics(openalex_id)
  df_ego$h_index[i] <- metrics$h_index
  df_ego$i10_index[i] <- metrics$i10_index
  df_ego$works_count[i] <- metrics$works_count
  df_ego$cited_by_count[i] <- metrics$cited_by_count
}

# View updated df_ego with h-index and i10-index
view(df_ego[c('au_id','Naam','gender','h_index','i10_index')])

@@

# Quick RSiena

```{r RSiena}
#step1 data
wave1 <- test$nets[1,,]
wave2 <- test$nets[2,,]

#put diagonals to zero 
diag(wave1) <- 0
diag(wave2) <- 0
# we want a binary tie (not a weighted tie)
wave1[wave1 > 1] <- 1
wave2[wave2 > 1] <- 1
```

```{r RSiena2}
# put the nets in an array
net_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))
#dependent
nets <- sienaDependent(net_array)

#put gender in object 
gender <- df_ego$gender
#covariate
gender_RS <- coCovar(gender) # gender as covariate in Rsiena

#put h-index in object 
h_index <- df_ego$h_index
df_ego$h_index
#covarite 2
h_index_RS <- coCovar(h_index) # h_index as covariate in RSiena

#define data 
mydata <- sienaDataCreate(nets, gender_RS, h_index_RS)

#define effects structure 
myeff <- getEffects(mydata)

# skipped initial description part

myeff <- includeEffects(myeff, isolateNet, inPop, outAct)

myeff <- includeEffects(myeff, egoX, altX, sameX, interaction1 = "gender_RS")
#include effect of h index later too etc
#look up which effects to iclude

myAlgorithm <- sienaAlgorithmCreate(modelType = c(nets=6), projname = "proProject")
# undirected: model 6 "additive model", #check manual for this
```

```{r RSiena-model estimate}
# estimate the model 
model1 <- siena07(myAlgorithm, data = mydata, effects = myeff, returnDeps = TRUE)
#latter needed for GOF

model1

# output:  convergence ration NA probably bc we chose all ties to be included (type = "all") earlier
# we can go back and change that or change it here in the myAlgorithm function

# Make it a directed network 
# focus: writing, h index, 
# model interpretation

# Plotting
```{r}
test_w1 <- igraph::graph_from_adjacency_matrix(
  test$nets[1,,], # first wave of data. 
  # (thus I select the array of networks and take the first matrix)
  mode = c("directed"),
  weighted = NULL,
  diag = FALSE,
  add.colnames = NULL,
  add.rownames = NULL)

```{r}
names(df_ego) #see labels of variables

plot(test_w1,
vertex.color = ifelse(df_ego$gender == 1, "red", "blue"), # now, I can use actor attributes for plotting.
# here: if gender = 1 (aka man) then red dot, if not then blue 
vertex.label = NA,
edge.width = 0.2,
edge.arrow.size =0.2)

# if you dont want plot to turn, save the layout (look at SNASS)
```

>>>>

---
title: "Descriptive adventures"
author: "Verooo"
date: "2024-11-08"
output: html_document
---

@@

Scholar

```{r scholar data}
scholars <- fload("./data/processed/scholars_20240924.rda") 
#make sure to lead fload first of course
```

```{r saving schoalr output}
# save the output of your function

@@

# USE not all but first or last so the ties are directed from "perspective" of first author of the publications 
# usually first author has most prestige
```

Ego

```{r df_ego data}
df_ego <- fload("./data/processed/df_ego_20241108.rda")
```

```{r matrix data ego}

test_w1 <- igraph::graph_from_adjacency_matrix(
  test$nets[1,,], # first wave of data. 
  # (thus I select the array of networks and take the first matrix)
  mode = c("directed"),
  weighted = NULL,
  diag = FALSE,
  add.colnames = NULL,
  add.rownames = NULL)

@@

# Descriptives

## Ego level

### Gender

-   Gender

    -   descriptives (mean etc.)

```{r sum gender}
summary(df_ego$gender)

@@

    -   overall

```{r hist gender}
# Histogram of prestige scores for Wave 1  
hist(df_ego$gender, breaks = , main = "Distribution of gender",     xlab = "Gender", ylab = "Frequency", col = "#B3DE69") # INSERT YEARS OF WAVE/TIME FRAME STILL
```

```         
-   Gender per department
```

```{r gender per dep.}
# STILL DO 
```

### h index

```         
-   descriptives (mean etc.)
```

```{r sum h index}
summary(df_ego$h_index) 
```

```         
- Overall  (INSERT YEARS STILL)
```

```{r hist h index}

# Histogram of prestige scores for Wave 1 
hist(df_ego$h_index, breaks = 30, main = "Distribution of H-Index from yearX to yearX",     xlab = "H Index", ylab = "Frequency", col = "#B3DE69") # INSERT YEARS OF WAVE/TIME FRAME STILL
```

```         
-   H index per department
```

```{r h index per dep.}
# STILL DO 
```

## Ego network

### basic descriptives

-   Nr. of nodes

```{r nodes}
vcount(test_w1)
```

-   Nr. of edges

```{r edges}
ecount(test_w1)
```

-   Dyad census

    ```{r dyad cen}
    # still do 
    ```

-   Triad-census

    ```{r triad cen}
    # still do 
    ```

-   edge-density

    ```{r edge dens}
    #still do 
    ```

### more indepth:

-   reciprocity

    ```{r recip}
    #still do 
    ```

-   degree centrality / degreee?

    ```{r degree}
    # still do 
    ```

-   Betweenness centrality /betweenness?

    ```{r betweenness}
    #still do 
    ```

-   Clustering

    ```{r clustering}
    #still do 
    ```

## Network-level descriptives

-   Density

    ```{r density}
    #still do 
    ```

-   Average path length

    ```{r path length}
    # still do 
    ```

-   Segregation

    -   Mortons I
    -   igraphs
    -   ggraphs

```{r plot}

```{r plot gender}
names(df_ego) #see labels of variables

plot(test_w1,
vertex.color = ifelse(df_ego$gender == 1, "#FB8072", "#80B1D3"), # now, I can use actor attributes for plotting.
# here: if gender = 1 (aka man) then red dot, if not then blue 
vertex.label = NA,
edge.width = 0.2,
edge.arrow.size =0.2)

# if you dont want plot to turn, save the layout (look at SNASS)

@@

# Detour: Colors

```{r mypalette, include = FALSE, eval = FALSE}
# palette i like:
palette("Set 3");  sinplot("Set 3")
palette.swatch("Set 3")
palette.colors(palette = "Set 3")
 "#8DD3C7" "#FFFFB3" "#BEBADA" "#FB8072" "#80B1D3" "#FDB462"
 "#B3DE69" "#FCCDE5" "#D9D9D9" "#BC80BD" "#CCEBC5" "#FFED6F"
```

```{r colors in R, include = FALSE, eval = FALSE}
colors (distinct = TRUE) # prints all colors R knows
palette.pals()
#  [1] "R3"              "R4"              "ggplot2"        
#  [4] "Okabe-Ito"       "Accent"          "Dark 2"         
#  [7] "Paired"          "Pastel 1"        "Pastel 2"       
# [10] "Set 1"           "Set 2"           "Set 3"          
# [13] "Tableau 10"      "Classic Tableau" "Polychrome 36"  
# [16] "Alphabet"

palette.colors(palette = "-palette name here-")
# [1] "#000000" "#E69F00" "#56B4E9" "#009E73" "#F0E442" "#0072B2"
# [7] "#D55E00" "#CC79A7" "#999999"
```

```{r look at colors PLOT, include = FALSE, eval = FALSE}
## Demonstrate the colors 1:8 in different palettes using a custom matplot()
sinplot <- function(main=NULL, n = 8) {
    x <- outer(
	seq(-pi, pi, length.out = 50),
	seq(  0, pi, length.out = n),
	function(x, y) sin(x - y)
    )
    matplot(x, type = "l", lwd = 4, lty = 1, col = 1:n, ylab = "", main=main)
}
sinplot("default palette")

palette("R3");        sinplot("R3")
palette("Okabe-Ito"); sinplot("Okabe-Ito")
palette("Tableau")  ; sinplot("Tableau", n = 10) # i like 
palROB <- colorRampPalette(c("red", "darkorange2", "blue"), space = "Lab")
palette(palROB(16)); sinplot("palROB(16)", n = 16) # the orange purple blue rainbow retro vibe yay 
palette("default") # reset
```

```{r look at colors SWATCH, include = FALSE, eval = FALSE}
palette.swatch <- function(palette = palette.pals(), n = 8, nrow = 8,
                           border = "black", cex = 1, ...)
{
     cols <- sapply(palette, palette.colors, n = n, recycle = TRUE)
     ncol <- ncol(cols)
     nswatch <- min(ncol, nrow)
     op <- par(mar = rep(0.1, 4),
               mfrow = c(1, min(5, ceiling(ncol/nrow))),
     	       cex = cex, ...)
     on.exit(par(op))
     while (length(palette)) {
 	subset <- seq_len(min(nrow, ncol(cols)))
 	plot.new()
 	plot.window(c(0, n), c(0.25, nrow + 0.25))
 	y <- rev(subset)
 	text(0, y + 0.1, palette[subset], adj = c(0, 0))
 	y <- rep(y, each = n)
 	rect(rep(0:(n-1), n), y, rep(1:n, n), y - 0.5,
 	     col = cols[, subset], border = border)
 	palette <- palette[-subset]
 	cols    <- cols [, -subset, drop = FALSE]
     }
}

palette.swatch()

palette.swatch(n = 26) # show full "Alphabet"; recycle most others

@@

### 2024-11-09 weekbacktrack.Rmd
restructuredprepdescriptivesandrsiena

+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------+

@@

+:==============================================================================================+:===========================================================+:==============================================================+:===========================================================================================+:================================================================+:==========================================================================+:========================================================+

@@

| ![](images/socialnetworking_meh.jpg){width="800"}\                                            | ![](images/used_arson%20frog.jpg){width="952"}[work]       | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking.jpg){width="800"}rewrite intro and Theory [W] | ![](images/timetopanic.gif){width="800"}[Grandmas bday] |
| fix package error,                                                                            |                                                            |                                                               | Read Jochems answer & revisit RQs                                                          | Initial description [S3]                                        |                                                                           |                                                         |
|                                                                                               | Talk to Jochem                                             |                                                               |                                                                                            |                                                                 | Specify model [S4]                                                        |                                                         |
| Define variables (get stuck with sienaDependent)                                              |                                                            |                                                               | & create effects structure [S2]                                                            | Plotting& Revisit RQs                                           |                                                                           |                                                         |

@@

| check in with Jochem                                                                          |                                                            |                                                               | Plotting & revisit RQs                                                                     |                                                                 |                                                                           |                                                         |

@@

| Plotting                                                                                      |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                         |
+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------+

@@

| ![](images/socialnetworking_meh.jpg){width="800"}Data & methods part [W]                      | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking.jpg){width="800"}Data & methods part [W]\                      | ![](images/socialnetworking.jpg){width="800"}estimate model     | ![](images/socialnetworking.jpg){width="800"}goodness of fit [S6]         | ![](images/kermit-panic.gif)                            |

@@

| Check in with Jochem                                                                          |                                                            |                                                               |                                                                                            | Plotting                                                        | Start Results [W]                                                         | [chores at home and university]                         |
+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------+

>>>>

+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------------------+

@@

+:==============================================================================================+:===========================================================+:==============================================================+:===========================================================================================+:================================================================+:==========================================================================+:====================================================================+

@@

| ![](images/socialnetworking_meh.jpg){width="800"}\                                            | ![](images/used_arson%20frog.jpg){width="952"}[work]       | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking.jpg){width="800"}rewrite intro and Theory [W] | ![](images/timetopanic.gif){width="800"}[Grandmas bday celebration] |
| fix package error,                                                                            |                                                            |                                                               | Read Jochems answer & revisit code                                                         | fix bugging webjournal                                          |                                                                           |                                                                     |
|                                                                                               | Talk to Jochem                                             |                                                               |                                                                                            |                                                                 | read into specifying model [S4]                                           |                                                                     |
| Define variables (get stuck with sienaDependent)                                              |                                                            |                                                               | & create effects structure [S2]                                                            | journal, make submenus                                          |                                                                           |                                                                     |

@@

| check in with Jochem                                                                          |                                                            |                                                               | make h index                                                                               | Reorganize code                                                 |                                                                           |                                                                     |

@@

| Plotting                                                                                      |                                                            |                                                               |                                                                                            | Starting with initial description [S3]                          |                                                                           |                                                                     |
|                                                                                               |                                                            |                                                               |                                                                                            | Plotting                                                        |                                                                           |                                                                     |
+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------------------+

@@

| ![](images/socialnetworking_meh.jpg){width="800"}Write Data & methods part [W]                | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking.jpg){width="800"}Data & methods part [W]\                      | ![](images/socialnetworking.jpg){width="800"}estimate model     | ![](images/socialnetworking.jpg){width="800"}goodness of fit [S6]         | ![](images/kermit-panic.gif)                                        |

@@

| Check in with Jochem                                                                          |                                                            |                                                               |                                                                                            | goodness of fit                                                 | Start Results [W]                                                         | [chores at home and university]                                     |
+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------------------+
